Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Remove comment
Terminology.

\begin{quote}
    TBD: ``Section'' to ``section''

kazu: ``Section X.Y'' is perfect English, i.e. a proper noun.
      ``The following three sections'' is also perfect, i.e. a ordinal noun.
\end{quote}

@@

\item[property]
    Property means a QuickCheck property as defined in~\cite{quickcheck}.

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
\end{quote}

>>>>

@@

\item[property]
    A property is something that is testable with
    QuickCheck~\cite{quickcheck}.

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
\end{quote}
